DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-26 paper/comparison.tex
Change figure sizes
Many of the figures were relatively small and hard to see, so the sizes
were increased.
Update platform comparison section

@@

Our basic approach is to use the same DeepPicar software, and repeat
the experiments in Section~\ref{sec:evaluation} on each hardware
platform and compare the results. 
For the Jetson TX2, we have two different system configurations,
which differ in whether TensorFlow is configured to use its GPU or
only the CPU cores. Thus, the total four system configurations are
compared.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_core}
  \caption{Average control loop execution time.} 
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Jetson TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while the TX2 (CPU) and TX2 (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin,
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that TX2
(GPU) does not change much, as most of the neural network computation
is done at the GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_model}
  \caption{Average control loop execution time when multiple DNN
    models are co-scheduled. }
  \label{fig:sys_model}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_benchmark}
  \caption{Average control loop execution time in the presence of an
    increasing number of memory intensive applications on idle CPU cores.}
  \label{fig:sys_bench}
\end{figure}

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results.
As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 9.4X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in the Intel Up and Jetson TX2, but the degree of the increase is 
not as dramatic as the Pi 3. Compared to their respective solo timings 
(i.e., the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.5X increases, respectively. This is somewhat suprising
because the Raspberry Pi 3's cores are in-order architecture based while
the cores in the Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We suspect that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
bandwidth and fairness than the memory subsystem of the Pi 3.

Another interesting observation is that the TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms where both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, the TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there was no contention between the CPU cores and the GPU.

>>>>

\begin{table*}[h]
  \centering
  \begin{adjustbox}{width=1\textwidth}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra X2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
	Peak Memory Bandwidth & 8.5 GB/s & 12.8 GB/s & 59.7 GB/s \\
	\hline
	Measured Bandwidth & 2127.94 MB/s & 3951.94 MB/s & 4447.90 MB/s \\
	\hline
  \end{tabular}
  \end{adjustbox}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}

@@

Our basic approach is to use the same DeepPicar software, and repeat
the experiments in Section~\ref{sec:evaluation} on each hardware
platform and compare the results. We do not, however, repeat the cache
partitioned experiments done on the Pi 3, as we did not believe our 
findings warranted further experimentation on additional platforms. 
For the Jetson TX2, we have two different system configurations,
which differ in whether TensorFlow is configured to use its GPU or
only the CPU cores. Thus, the total four system configurations are
compared.

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_core}
  \caption{Average control loop execution time.} 
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Jetson TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 1.33X faster than
the Pi 3, while the TX2 (CPU) and TX2 (GPU) are 2.79X and 4.16X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 33.$\overline{\mbox{33}}$ ms 
WCET by a clear margin,
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that TX2
(GPU) does not change much, as most of the neural network computation
is done at the GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_model}
  \caption{Average control loop execution time when multiple DNN
    models are co-scheduled. }
  \label{fig:sys_model}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_benchmark}
  \caption{Average control loop execution time in the presence of an
    increasing number of memory intensive applications on idle CPU cores.}
  \label{fig:sys_bench}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_l2missrate}
  \caption{L2 miss rates in the presence of an increasing number of 
			memory intensive applications on idle CPU cores.}
  \label{fig:sys_l2miss}
\end{figure}

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results.
As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 11.6X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in the Intel Up and Jetson TX2, but the degree of the increase is 
not as dramatic as the Pi 3. Compared to their respective solo timings 
(i.e., the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.1X increases, respectively. This is somewhat suprising
because the Raspberry Pi 3's cores are in-order architecture based while
the cores in the Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We suspect that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
bandwidth and fairness than the memory subsystem of the Pi 3.

However, the L2 miss rates of the platforms follow the same expected 
pattern, as can be seen in Figure~\ref{fig:sys_l2miss}. Namely, the 
percentage of L2 miss rates increases are more 
memory intensive co-runners are introduced. We found that the Pi 3 had 
slightly higher L2 miss rates than the TX2, both CPU and GPU, but lower 
miss rates than the UP, which had the highest l2 miss rates. Also, we
found that the TX2 had similar miss rates when it used either the CPU
or the GPU, which was expected as the GPU on the TX2 shares a majority 
of the available DRAM.

Another interesting observation is that the TX2 (GPU) also suffers
considerable execution time increase (2.1X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms where both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, the TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there was no contention between the CPU cores and the GPU.
